Design and Implementation of Probabilistic Programming Language Anglican

### 2016-08-15 paper/paper.tex
update
added changebar and comments with brief instructions
simpler explanation of advantage of probabilistic programming

\usepackage{enumitem}
\usepackage[lighttt]{lmodern}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{graphicx}

@@

@@

@@

Probabilistic programming systems \cite{GMR+08,MSP14,WVM14,GS15}
represent generative models as programs written in a specialized
language that provides syntax for the definition and conditioning of
random variables. The code for such models is generally concise,
modular, and easy to modify or extend. Typically inference can be
performed for any probabilistic program using one or more generic
inference techniques provided by the system backend, such as
Metropolis-Hastings \cite{WSG11,MSP14,YHG14}, Hamiltonian Monte Carlo
\cite{SDT04}, expectation propagation \cite{MWG+10}, and extensions
of Sequential Monte Carlo \cite{WVM14,MYM+15,PWD+14} methods.
Although these generic techniques are not always as statistically
efficient as techniques that take advantage of model-specific
optimizations, probabilistic programming makes it easier to optimize
models for a specific application in a manner that is efficient in
terms of the dimensionality of its latent variables.

\hy{Minor point. I got slightly confused by the last sentence. What does
``efficient in terms of the dimensionality ..'' mean?}

@@

In this paper, we presented design and implementation internals
of the Probabilistic Programming System Anglican. Implementing
a language is an interesting endeavour, in particular when the
language implements a new paradigm, in this case probabilistic
programming. Functional programming is a natural complement of
probabilistic programming --- the latter allows both concise and
expressive specification of probabilistic generative models and
efficient implementation of inference algorithm.

>>>>

\usepackage[color]{changebar}
\usepackage{enumitem}
\usepackage[lighttt]{lmodern}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{graphicx}

@@

% Authors: comment using these commands

@@

% Authors: use changebars to mark changed regions
% \cbstart
% ...
% \cbend

@@

Probabilistic programming systems \cite{GMR+08,MSP14,WVM14,GS15}
represent generative models as programs written in a specialized
language that provides syntax for the definition and conditioning of
random variables. The code for such models is generally concise,
modular, and easy to modify or extend. Typically inference can be
performed for any probabilistic program using one or more generic
inference techniques provided by the system backend, such as
Metropolis-Hastings \cite{WSG11,MSP14,YHG14}, Hamiltonian Monte Carlo
\cite{SDT04}, expectation propagation \cite{MWG+10}, and extensions
of Sequential Monte Carlo \cite{WVM14,MYM+15,PWD+14} methods.
% Although these generic techniques are not always as statistically
% efficient as techniques that take advantage of model-specific
% optimizations, probabilistic programming makes it easier to optimize
% models for a specific application in a manner that is efficient in
% terms of the dimensionality of its latent variables.
\cbstart
These generic techniques may be less statistically efficient
than techniques tailored to a specific model, however
probabilistic programming facilitates simpler implementations of
models making the inference inherently faster.
\cbend

%\hy{Minor point. I got slightly confused by the last sentence. What does
%``efficient in terms of the dimensionality ..'' mean?}

@@

In this paper, we presented design and implementation internals
of the \emph{probabilistic programming system} Anglican. Implementing
a language is an interesting endeavour, in particular when the
language implements a new paradigm, in this case probabilistic
programming. Functional programming is a natural complement of
probabilistic programming --- the latter allows both concise and
expressive specification of probabilistic generative models and
efficient implementation of inference algorithm.
